Typed Lua

### 2013-06-17 doc/slides/gsoc_proposal/gsoc_proposal.tex
Added more information to the presentation about the GSoC proposal

\subsection{Gradual Typing and Dynamically Typed Languages}
\begin{frame}
\frametitle{Gradual Typing and Dynamically Typed Languages}
\begin{itemize}
\item Dart and TypeScript
\begin{itemize}
\item New languages derived from JavaScript
\item Both target JavaScript
\item Both are designed with a gradual typing system
\end{itemize}
\item Typed Scheme, Typed Racket, and core.typed
\begin{itemize}
\item Gradual typing extensions to Scheme, Racket, and Clojure
\end{itemize}
\item Perl
\item Python
\item Ruby
\end{itemize}
\end{frame}

\section{Typed Lua}
\begin{frame}
\frametitle{Typed Lua}
\begin{itemize}
\item A proposal to design a gradual type system for Lua
\begin{itemize}
\item Should be simple enough to preserve existent Lua idioms
\end{itemize}
\item Superset of Lua
\begin{itemize}
\item Type annotations
\item Compile-time type checking
\item Classes
\item Interfaces
\item Modules
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Typed Lua}
\begin{itemize}
\item Lua X OO programming and modules
\begin{itemize}
\item It is possible to write OO code in Lua
\item It is possible to split Lua code into modules
\item Does not set policies on how these features should behave
\item Due to its use as an embedded and extension language
\end{itemize}
\item Typed Lua intended usa is as an application language
\item So the policies for OO and modules should be part of the language
\item The gradual type system should also enforce these policies
\end{itemize}
\end{frame}

\subsection{Related Work}
\begin{frame}
\frametitle{Related Work}
\begin{itemize}
\item Some Lua projets implement parts of what is being proposed
\item However, none of them implement type checking along with OO programming
\item LuaInspect
\begin{itemize}
\item A tool that performs code analysis
\item For instance, flagging undeclared identifiers
\item It does not try to analyse OO code
\item It does not perform type checking
\end{itemize}
\item MetaLua and MoonScript
\begin{itemize}
\item Both support some sort of OO programming
\item However, both of them do not perform compile-time type checking
\end{itemize}
\item Tidal Lock
\begin{itemize}
\item A prototype of a gradual type system for Lua
\item It is not typing the common OO idioms used by Lua programmers
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\subsection{Gradual Typing and Dynamically Typed Languages}
\begin{frame}
\frametitle{Gradual Typing and Dynamically Typed Languages}
\begin{itemize}
\item Dart and TypeScript
\begin{itemize}
\item New languages derived from JavaScript
\item Both target JavaScript
\item Both are designed with a gradual typing system
\end{itemize}
\item Typed Scheme, Typed Racket, core.typed, and StrongRuby
\begin{itemize}
\item Gradual typing extensions to Scheme, Racket, Clojure, and Ruby
\end{itemize}
\item Perl 6
\begin{itemize}
\item Not compatible with Perl 5
\end{itemize}
\item Python
\begin{itemize}
\item gradual (package)
\item Run-time type checking semantics of gradual typing
\item Works only on Python 3
\end{itemize}
\end{itemize}
\end{frame}

\section{Typed Lua}
\begin{frame}
\frametitle{Typed Lua}
\begin{itemize}
\item A proposal to design a gradual type system for Lua
\begin{itemize}
\item Should be simple enough to preserve existent Lua idioms
\end{itemize}
\item A superset of Lua
\begin{itemize}
\item Type annotations
\item Compile-time type checking
\item Classes
\item Interfaces
\item Modules
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Typed Lua}
\begin{itemize}
\item Lua X OO programming and modules
\begin{itemize}
\item It is possible to write OO code in Lua
\item It is possible to split Lua code into modules
\item Does not set policies on how these features should behave
\item Due to its use as an embedded and extension language
\end{itemize}
\item Typed Lua intended use is as an application language
\item So the policies for OO and modules should be part of the language
\item The gradual type system should also enforce these policies
\end{itemize}
\end{frame}

\subsection{Related Work}
\begin{frame}
\frametitle{Related Work}
\begin{itemize}
\item Some Lua projects implement parts of what is being proposed
\item However, none of them implement type checking along with OO programming
\item LuaInspect
\begin{itemize}
\item A tool that performs code analysis
\item For instance, flagging undeclared identifiers
\item It does not try to analyze OO code
\item It does not perform type checking
\end{itemize}
\item MetaLua and MoonScript
\begin{itemize}
\item Both support some sort of OO programming
\item However, both of them do not perform compile-time type checking
\end{itemize}
\item Tidal Lock
\begin{itemize}
\item A prototype of a gradual type system for Lua
\item It is not typing the common OO idioms used by Lua programmers
\end{itemize}
\end{itemize}
\end{frame}
